---
title: "FML Assignment 3"
author: "Nikitha Chigurupati"
date: "2022-10-16"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
#IMPORTING THE DATASET
```{r}
Df <- read.csv("C:/Users/Nikitha/Downloads/UniversalBank.csv")
```

#CONVERTING THE PREDICTOR ATTRIBUTE TO FACTORS
```{r}
Df$Personal.Loan <- as.factor(Df$Personal.Loan)
Df$Online <- as.factor(Df$Online)
Df$CreditCard <- as.factor(Df$CreditCard)
```

#CHECKING FOR NULL VALUES
```{r}
sum(is.na(Df))
```

#LOADING THE LIBRARIES
```{r}
library(class)
library(caret)
library(e1071)
library(dplyr)
library(ggplot2)
library(reshape)
library(melt)
library(ISLR)
library(reshape2)
library(readr)
library(naivebayes)
library(pROC)
```

#DATA PARTITION TO 60:40
```{r}
set.seed(123)
datapart <- createDataPartition(Df$Personal.Loan,p=.6, list=F)
Train <- Df[datapart,]
Validate <- Df[-datapart,]
```

#DATA NORMALIZATION
```{r}
norm_model <- preProcess(Train[,-c(10,13:14)], 
                method=c("center","scale"))
Train_norm <- predict(norm_model,Train)
Validate_norm <- predict(norm_model,Validate)
```

#A. Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable
```{r}
tab1<- ftable(Train_norm[,c(14,10,13)])
tab1
```

#B. This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)] = 51/(51+467) = 0.0984.

#C. Creating two separate pivot tables for the training data. One having Loan (rows) as a function of Online (columns) and the other having Loan (rows) as a function of CC
```{r}
melt1 = melt(Train, id=c("CreditCard","Personal.Loan"), variable = "Online")
castbank = dcast(melt1, CreditCard+Personal.Loan~Online)
castbank[,c(1:2,14)] 
```

#D.Compute the following quantities [P(A | B) i.e. the probability of A given B]
```{r}
ftable(Train_norm[,c(10,13)])
```

```{r}
ftable(Train_norm[,c(10,14)])
```

```{r}
ftable(Train_norm[,10])
```

#1. P(CC = 1 | Loan = 1) = (84/84+204) = 0.291
#2. P(Online = 1 | Loan = 1)  = (176/176+112) = 0.611
#3. P(Loan = 1) = (288/288+2712) = 0.096
#4. P(CC = 1 | Loan = 0) = (777/777+1935) = 0.286
#5. P(Online = 1 | Loan = 0) = (1611/ 1611+1101) = 0.595
#6. P(Loan = 0) = (2712/ 2712+288) = 0.904

#E. Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1, Online = 1)
```{r}
#(0.291 x 0.611 x 0.096) / (0.271 x 0.611 x 0.096) + (0.286 x 0.595 x 0.904) = 0.1000
```

#F. We can see that the values attained in steps b, 0.0984, and a, 0.1000, are practically identical, although the probability with Naive Bayes is slightly higher.

#G. Run the Naive Bayes Model on the data
```{r}
Naive <- naive_bayes(Personal.Loan~Online+CreditCard,data=Train_norm)
Naive
#Naive Bayes Model results for the consumer taking the loan, using their credit card, and using online banking are 0.1000, which is equivalent to the result in E.
```

#Examining the AUC value and ROC curve
```{r}
Naive <- naiveBayes(Personal.Loan~Online+CreditCard,data=Train_norm)
Naive

predlab <- predict(Naive,Validate_norm,type = "raw")
head(predlab)
roc(Validate_norm$Online,predlab[,2])
plot.roc(Validate_norm$Online,predlab[,2])

```


